Discrete Quantum Theories and Computing

### 2018-04-09 dissertation.tex
CV_thesis.pdf Fix typos...
dissertation.lyx acknowledgments Updates...

@@

In common practice, randomized algorithms are approximated using a
pseudorandom number generator in place of a true source of random
bits; such an implementation may deviate from the expected theoretical
behavior~\cite{wiki:RandomizedAlgorithm}.

>>>>

Thank Hao-Chun Lee and Hsien-Ching Kao for discussing what I did in
the prospective of a general Ph.D. in Physics, and working later in
more computational industry.

@@
